Topology of the $O(3)$ non-linear sigma model under the gradient flow

### 2021-10-28 proceedings/draft.tex
fix bibliography issues
fix: small edit

% Please make sure you insert your
% data according to the instructions in PoSauthmanual.pdf
\documentclass[a4paper,11pt]{article}
\usepackage{pos}
% \usepackage{eulervm}
% \usepackage{xspace}
% \usepackage{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption}
\newcommand{\e}{\vec e}
\newcommand{\logchi}{7.4 }
\newcommand{\powchi}{8.8 }
\graphicspath{{../figures/}}
\newcommand\chris[1]{\textcolor{teal}{CJM: #1}}
\newcommand\stuart[1]{\textcolor{pink}{SNT: #1}}

@@

        \draw[-stealth] (1,0.5) -- (3,2.5);
        \draw[-stealth] (3.8,3) -- (3.8,1);
        \draw[-stealth] (3,0.2) -- (1,0.2);
    \end{tikzpicture}
    \caption{Visualization of a plaquette $x^*$. The dotted line separates the plaquette into two signed areas, used to define the topological charge density $q(x^*)$. Arrows represent the order of signed area.}
    %\caption{\label{fig:plaquette} Visualization of plaquette $x^*$. The dotted line separates the plaquette into two signed areas which are used to define the topological charge density $q(x^*)$. Arrows represent order of signed area.}
    \vspace*{-\baselineskip}
    \end{subfigure}
    \hspace*{1cm}
    \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.6, every node/.style={scale=1}]
        \pgfdeclarelayer{nodelayer}
        \pgfdeclarelayer{edgelayer}
        \pgfdeclareradialshading{sphere4}{\pgfpoint{-0.2cm}{0.5cm}}%
            {rgb(0cm)=(1,1,1);
            rgb(1cm)=(0.5,0.5,0.5); rgb(1.05cm)=(1,1,1)}
            %rgb(0.7cm)=(0.1,0.1,0.1); rgb(1cm)=(0.5,0.05,0); rgb(1.05cm)=(1,1,1)}
        \pgfsetlayers{nodelayer,edgelayer}
        \tikzstyle{label}=[fill=none, draw=none, shape=circle]
        \tikzstyle{point}=[inner sep=0pt, minimum size=0.2cm,fill=black, draw, shape=circle]
        %\tikzstyle{interior line}=[{Stealth[scale=1.5]}-,dotted,thick]
        \tikzstyle{interior line}=[dotted,thick]

@@

We can choose any flow time equation that drives the field towards a classical minimum. Following \cite{bietenholz2018}, we can define the gradient flow for the NLSM via the differential equation
\begin{equation}
    \label{eq:nsm_gradflow}
  \partial_\tau \e (\tau,x) = \left( 1 - \e(\tau,x) \e(\tau,x)^T \right) \partial^2 \e(\tau,x).
\end{equation}
We solve this equation numerically using the boundary condition $\e(\tau=0,x) = \e(x)$, a process described in Sec.~\ref{sec:numerics}.

@@

We apply the gradient flow equation
\begin{equation}
    \partial_\tau \e (\tau, x) = \left( 1 - \e(\tau,x) \e(\tau,x)^T\right) \partial^2 \e(\tau,x),
\end{equation}
replacing the continuous Laplacian operator $\partial^2$ with a discrete analogue
\begin{equation*}
    \partial^2 \e(\tau,x) = \e(\tau, x+a \hat{t}) + \e(\tau,x-a\hat t) + \e(\tau, x+a \hat{x}) + \e(\tau,x-a\hat x) - 4 \e(t,x).
\end{equation*}

We numerically solve the ordinary differential equation in Eq.~\ref{eq:nsm_gradflow} using a fourth-order Runga-Kutta approximation. To increase the efficiency of this algorithm, we implement the step-doubling algorithm to adaptively adjust the step size. If the error of a Runge-Kutta step is greater than the tolerance, the same step is repeated with half the step size. Alternatively, if the error is less than half of the tolerance, the step size is doubled for the next calculation. Finally, if the step size is greater than the distance to the next measurement, that distance is used as the step size, using the normal value afterwards. Otherwise, the algorithm proceeds with the consistent step size.

>>>>

% Please make sure you insert your
% data according to the instructions in PoSauthmanual.pdf
\documentclass[a4paper,11pt]{article}
\usepackage{pos}
% \usepackage{eulervm}
% \usepackage{xspace}
% \usepackage{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption}
\newcommand{\e}{\vec e}
\newcommand{\logchi}{7.4 }
\newcommand{\powchi}{8.8 }
\graphicspath{{../figures/}}
\newcommand\chris[1]{\textcolor{teal}{CJM: #1}}
\newcommand\stuart[1]{\textcolor{pink}{SNT: #1}}
% \newcommand\chris[1]{}
% \newcommand\stuart[1]{}

@@

        \draw[-stealth] (1,0.5) -- (3,2.5);
        \draw[-stealth] (3.8,3) -- (3.8,1);
        \draw[-stealth] (3,0.2) -- (1,0.2);
    \end{tikzpicture}
    \caption{\label{fig:plaquette} Visualization of a plaquette $x^*$. The dotted line separates the plaquette into two signed areas, used to define the topological charge density $q(x^*)$. Arrows represent the order of signed area.}
    %\caption{\label{fig:plaquette} Visualization of plaquette $x^*$. The dotted line separates the plaquette into two signed areas which are used to define the topological charge density $q(x^*)$. Arrows represent order of signed area.}
    \vspace*{-\baselineskip}
    \end{subfigure}
    \hspace*{1cm}
    \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.6, every node/.style={scale=1}]
        \pgfdeclarelayer{nodelayer}
        \pgfdeclarelayer{edgelayer}
        \pgfdeclareradialshading{sphere4}{\pgfpoint{-0.2cm}{0.5cm}}%
            {rgb(0cm)=(1,1,1);
            rgb(1cm)=(0.5,0.5,0.5); rgb(1.05cm)=(1,1,1)}
            %rgb(0.7cm)=(0.1,0.1,0.1); rgb(1cm)=(0.5,0.05,0); rgb(1.05cm)=(1,1,1)}
        \pgfsetlayers{nodelayer,edgelayer}
        \tikzstyle{label}=[fill=none, draw=none, shape=circle]
        \tikzstyle{point}=[inner sep=0pt, minimum size=0.2cm,fill=black, draw, shape=circle]
        %\tikzstyle{interior line}=[{Stealth[scale=1.5]}-,dotted,thick]
        \tikzstyle{interior line}=[dotted,thick]

@@

We can choose any flow time equation that drives the field towards a classical minimum. Following \cite{bietenholz2018}, we can define the gradient flow for the NLSM via the differential equation
\begin{equation}
    \label{eq:nlsm_gradflow}
  \partial_\tau \e (\tau,x) = \left( 1 - \e(\tau,x) \e(\tau,x)^T \right) \partial^2 \e(\tau,x).
\end{equation}
We solve this equation numerically using the boundary condition $\e(\tau=0,x) = \e(x)$, a process described in Sec.~\ref{sec:numerics}.

@@

We apply the gradient flow equation (Eq.~\ref{eq:nlsm_gradflow}) replacing the continuous Laplacian operator $\partial^2$ with a discrete analogue
\begin{equation*}
    \partial^2 \e(\tau,x) = \e(\tau, x+a \hat{t}) + \e(\tau,x-a\hat t) + \e(\tau, x+a \hat{x}) + \e(\tau,x-a\hat x) - 4 \e(t,x).
\end{equation*}
and numerically solving the differential equation using a fourth-order Runga-Kutta approximation. To increase the efficiency of this algorithm, we implement the step-doubling algorithm to adaptively adjust the step size. If the error of a Runge-Kutta step is greater than the tolerance, the same step is repeated with half the step size. Alternatively, if the error is less than half of the tolerance, the step size is doubled for the next calculation. Finally, if the step size is greater than the distance to the next measurement, that distance is used as the step size, using the normal value afterwards. Otherwise, the algorithm proceeds with the consistent step size.
